<<<<<<< HEAD
---
output: 
  html_document: 
    keep_md: yes
---

```{r include=FALSE, eval=FALSE, echo=FALSE}
synapseClient::synapseLogin()
knit2synapse::storeAndKnitToFileEntity("./webAccess.Rmd", 
                                       parentId = "syn4892835", 
                                       fileName = "Web Access")
```

=======
>>>>>>> c68ab9da55b2d6b7b530442f7e96d14e671dfc3c
```{r libs, echo=FALSE, warning=FALSE, message=FALSE}
library(plyr)
library(dplyr)
library(reshape)
library(data.table)
library(xtable)
library(knitr)
library(ggplot2)
library(scales)
library(stringr)
library(synapseClient)
library(RMySQL)
library(yaml)
library(lubridate)

<<<<<<< HEAD
source("lib.R")

=======
>>>>>>> c68ab9da55b2d6b7b530442f7e96d14e671dfc3c
synapseLogin()

options(xtable.type="html")

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  fig.width=20)

mytheme <- theme_bw() + theme(axis.text=element_text(size=16),
                              axis.title.x=element_text(size=18),
                              axis.title.y=element_text(size=18, angle=90))

# Full header of table
header <- c("returnobjectid", "elapsems", "timestamp", "via", "host", "threadid", 
            "useragent", "querystring", "sessionid", "xforwardedfor", "requesturl", 
            "userid", "origin", "date", "method", "vmid", "instance", "stack",
            "success", "responsestatus")

# Columns we're interested in
keepcols <- c(1, 3, 7, 11, 12, 14, 18, 19)

```
```{r mysql}
<<<<<<< HEAD
config <- yaml.load_file("mysql_config.yml")

projectId <- '2862345'
=======
# The tables are set up by month

config <- yaml.load_file("mysql_config.yml")

projectId <- '1773109'
>>>>>>> c68ab9da55b2d6b7b530442f7e96d14e671dfc3c

con <- dbConnect(MySQL(),
                 user = config$username,
                 password = config$password,
                 host = config$host,
                 dbname='warehouse')

endDate <- as.POSIXct(Sys.Date(), origin="1970-01-01", tz="PST")
endTimestamp <- as.numeric(endDate) * 1000

beginDate <- endDate - months(1)
beginTimestamp <- as.numeric(beginDate) * 1000
<<<<<<< HEAD
# 
q.browse <- sprintf('select NORMALIZED_METHOD_SIGNATURE,PROJECT_ID,BENEFACTOR_ID,PARENT_ID,ENTITY_ID,CONVERT(AR.TIMESTAMP, CHAR) AS TIMESTAMP,RESPONSE_STATUS,DATE,USER_ID,NODE_TYPE,N.NAME from ACCESS_RECORD AR, PROCESSED_ACCESS_RECORD PAR, NODE_SNAPSHOT N, (select distinct ID from NODE_SNAPSHOT where PROJECT_ID = "%s") NODE where AR.TIMESTAMP Between %s AND %s and AR.SESSION_ID = PAR.SESSION_ID and AR.TIMESTAMP = PAR.TIMESTAMP and PAR.ENTITY_ID = NODE.ID and N.ID = NODE.ID and CLIENT = "WEB" AND (PAR.NORMALIZED_METHOD_SIGNATURE = "GET /entity/#/bundle" OR PAR.NORMALIZED_METHOD_SIGNATURE = "GET /entity/#/version/#/bundle" OR PAR.NORMALIZED_METHOD_SIGNATURE = "GET /entity/#/wiki2" OR PAR.NORMALIZED_METHOD_SIGNATURE = "GET /entity/#/wiki2/#");', projectId, beginTimestamp, endTimestamp)
=======

q.browse <- sprintf('select NORMALIZED_METHOD_SIGNATURE,PROJECT_ID,BENEFACTOR_ID,PARENT_ID,ENTITY_ID,N.TIMESTAMP,RESPONSE_STATUS,DATE,USER_ID,NODE_TYPE,N.NAME from ACCESS_RECORD AR, PROCESSED_ACCESS_RECORD PAR, NODE_SNAPSHOT N, (select distinct ID from NODE_SNAPSHOT where PROJECT_ID = "%s") NODE where AR.TIMESTAMP Between %s AND %s and AR.SESSION_ID = PAR.SESSION_ID and AR.TIMESTAMP = PAR.TIMESTAMP and PAR.ENTITY_ID = NODE.ID and N.ID = NODE.ID and CLIENT = "WEB" AND (PAR.NORMALIZED_METHOD_SIGNATURE = "GET /entity/#/bundle" OR PAR.NORMALIZED_METHOD_SIGNATURE = "GET /entity/#/version/#/bundle" OR PAR.NORMALIZED_METHOD_SIGNATURE = "GET /entity/#/wiki2" OR PAR.NORMALIZED_METHOD_SIGNATURE = "GET /entity/#/wiki2/#");', projectId, beginTimestamp, endTimestamp)
>>>>>>> c68ab9da55b2d6b7b530442f7e96d14e671dfc3c

data.browse <- dbGetQuery(conn = con, statement=q.browse) %>% 
  dplyr::rename(userid=USER_ID, id=ENTITY_ID)

<<<<<<< HEAD
foo <- data.browse %>% filter(RESPONSE_STATUS == 200)  %>% count(userid, id, DATE, TIMESTAMP, NODE_TYPE, NAME) %>% ungroup()

data.browse <- foo
```
### Web access usage statistics from `r as.Date(beginDate)` to `r as.Date(endDate)`.

```{r users}
# Get users at project level
aclUserList <- aclToUserList("syn2862345")
aclUserList$teamId <- factor(aclUserList$teamId, 
                             levels=c("syn2862345", 3323597, 3330234, 3332397),
                             ordered=TRUE)

aclUserList <- aclUserList %>%
  group_by(userId) %>% 
  arrange(teamId) %>% 
  slice(1) %>% 
  ungroup()

# # Get sage employees
# sageUserList <- getTeamMemberDF(273957)
# userList <- rbind(userList, sageUserList)

```

=======
```
### Web access usage statistics from `r as.Date(beginDate)` to `r as.Date(endDate)`.

```{r pcbcusers}
# Get users at project level
acl <- synGetEntityACL("syn1773109")

aclUserList <- ldply(acl@resourceAccess@content, 
                     function(x) data.frame(userid=as.character(x@principalId),
                                            teamid="syn1773109"))

# Get users as part of core bioinfo team
coreUserListREST <- synRestGET("/teamMembers/3319054?limit=100")
coreUserList <- ldply(coreUserListREST$results,
                      function(x) data.frame(userid=as.character(x$member$ownerId), 
                                             teamid=as.character(x$teamId)))

coreUserList <- coreUserList %>%
  filter(!(userid %in% aclUserList$userid))

# Get all PCBC users
pcbcUserListREST <- synRestGET("/teamMembers/2224090?limit=100")
pcbcUserList <- ldply(pcbcUserListREST$results, 
                      function(x) data.frame(userid=as.character(x$member$ownerId), 
                                             teamid=as.character(x$teamId)))

# Remove users in the PCBC group that are also in the ACL or core bioinfo group
pcbcUserList <- pcbcUserList %>%
  filter(!(userid %in% c(as.character(aclUserList$userid), 
                         as.character(coreUserList$userid))))

# Get sage employees
sageUserListREST <- synRestGET("/teamMembers/273957?limit=100")
sageUserList <- ldply(sageUserListREST$results,
                      function(x) data.frame(userid=as.character(x$member$ownerId), 
                                             teamid=as.character(x$teamId)))

sageUserList <- sageUserList %>%
  filter(!(userid %in% c(as.character(aclUserList$userid), 
                         as.character(coreUserList$userid),
                         as.character(pcbcUserList$userid))))

allKnownUsers <- rbind(aclUserList, coreUserList, pcbcUserList, sageUserList)
```
>>>>>>> c68ab9da55b2d6b7b530442f7e96d14e671dfc3c
```{r summaryuseraccess}
# Get user profile info for users in data download records
allUsersList <- ldply(unique(data.browse$userid),
                      function(x) {
                        foo <- synGetUserProfile(x); 
<<<<<<< HEAD
                        data.frame(userId=as.character(x),
                                   userName=foo@userName)})

allUsers <- left_join(allUsersList, aclUserList)
levels(allUsers$teamId) <- c(levels(allUsers$teamId), "None") 
allUsers$teamId[is.na(allUsers$teamId)] <- "None"

allUsers$group <- "Other"
teamInfo <- ddply(allUsers %>% filter(teamId != "None") %>% select(teamId) %>% unique(),
                  .(teamId),
                  function(x) {
                    tmp <- synRestGET(sprintf("/team/%s", x$teamId)); 
                    data.frame(teamId=x$teamId, teamName=tmp$name)
                    }
                  )


allUsers <- left_join(allUsers, teamInfo, by="teamId")
levels(allUsers$teamName) <- c(levels(allUsers$teamName), "None") 
allUsers$teamName[is.na(allUsers$teamName)] <- "None"
```

=======
                        data.frame(userid=as.character(x),
                                   username=foo@userName)})

allUsers <- left_join(allUsersList, allKnownUsers)

allUsers$group <- "Other"
allUsers$group[allUsers$teamid %in% c("syn1773109", "3319054", "2224090")] <- "PCBC"
allUsers$group[allUsers$teamid %in% c("273957")] <- "Sage"
allUsers$group <- factor(allUsers$group, levels=c("PCBC", "Sage", "Other"), ordered=TRUE)
```
>>>>>>> c68ab9da55b2d6b7b530442f7e96d14e671dfc3c
#### Website access per day
```{r loadperday, include=TRUE, eval=TRUE}
### Daily usage
data.browse <- data.browse %>%
  mutate(date=as.Date(as.character(DATE)),
<<<<<<< HEAD
         userId=as.character(userid)) %>% 
  left_join(., allUsers)

perdayCount <- data.browse %>%
  count(teamName, date) %>% 
  arrange(n)
```

```{r plotperday, fig.width=20, fig.height=6, include=TRUE, eval=TRUE}
### Per day usage, total
plotdata <- perdayCount %>% 
  dcast(date ~ teamName, value.var='n', fill=0) %>% 
  reshape::melt(., id.vars=c("date"), 
                variable.name="teamName", value.name="n") %>% 
  dplyr::rename(group=variable, n=value)

p <- ggplot(plotdata, aes(x=date, y=n)) + geom_line(aes(group=group, color=group), size=1)
p <- p + scale_color_brewer(palette = "Set1")
# p <- p + scale_x_date(breaks = "1 week", minor_breaks = "1 day",
#                       labels = date_format("%b-%Y"),
#                       limits = c(as.Date(beginDate), as.Date(endDate)))
p  <- p + mytheme + theme(axis.title.x=element_blank(),
                          axis.text.x=element_text(size=16, angle=270),
                          legend.position="top")
=======
         userid=as.character(userid)) %>% 
  left_join(., allUsers) %>% 
  filter(!is.na(group))

perdayCount <- data.browse %>%
  count(group, date) %>% 
  arrange(n)
```
```{r plotperday, fig.width=20, fig.height=6, include=TRUE, eval=TRUE}
### Per day usage, total
plotdata <- perdayCount %>% 
  dcast(date ~ group, value.var='n', fill=0) %>% 
  reshape::melt(., id.vars=c("date"), variable.name="group", value.name="n") %>% 
  dplyr::rename(group=variable, n=value)

p <- ggplot(plotdata, aes(x=date, y=n)) + geom_line(aes(group=group, color=group), size=1)
p <- p + scale_x_date(breaks = "1 week", minor_breaks = "1 day",
                      #labels = date_format("%b %Y"),
                      limits = c(as.Date(beginDate), as.Date(endDate)))
p  <- p + mytheme + theme(axis.title.x=element_blank(),
                          axis.text.x=element_text(size=16, angle=270))
>>>>>>> c68ab9da55b2d6b7b530442f7e96d14e671dfc3c
p
```
```{r include=TRUE, eval=TRUE}
### Users
useraccessCount <- data.browse %>% 
<<<<<<< HEAD
  count(userName, userId, teamId, teamName) %>% 
  ungroup() %>%
  arrange(n) %>%
  mutate(userName=reorder(userName, n, order=TRUE),
         userId=reorder(userId, n, order=TRUE))
```

#### Accesses per day per user
```{r plotperdayperuser, fig.width=20, fig.height=6, include=TRUE, eval=TRUE}
plotdata <- data.browse %>%
  group_by(teamName) %>% 
  count(date, userName, userId, teamName) %>% 
  ungroup()

p <- ggplot(plotdata, aes(x=date, y=n, color=teamName))
p <- p + geom_point(size=3, position = position_jitter(w = 0, h = 0.1))
# p <- p + scale_x_date(breaks = "1 week", minor_breaks = "1 day",
#                       # labels = date_format("%b %Y"),
#                       limits = c(as.Date(beginDate), as.Date(endDate)))
=======
  count(username, userid, teamid, group) %>% 
  ungroup() %>%
  arrange(n) %>%
  mutate(username=reorder(username, n, order=TRUE),
         userid=reorder(userid, n, order=TRUE))
```

#### Accesses per day per user

```{r plotperdayperuser, fig.width=20, fig.height=6, include=TRUE, eval=TRUE}
plotdata <- data.browse %>%
  group_by(group) %>% 
  count(date, username, userid, group) %>% 
  ungroup()

p <- ggplot(plotdata, aes(x=date, y=n, color=group)) + geom_point(size=3, position = position_jitter(w = 0, h = 0.1))
p <- p + scale_x_date(breaks = "1 week", minor_breaks = "1 day",
                      # labels = date_format("%b %Y"),
                      limits = c(as.Date(beginDate), as.Date(endDate)))
>>>>>>> c68ab9da55b2d6b7b530442f7e96d14e671dfc3c
p <- p + scale_color_brewer(palette = "Set1")
p <- p + scale_y_log10()
p  <- p + labs(y=expression(log[10]("access per user")), x="Day")
# p <- p + facet_grid(group ~ .)
p  <- p + mytheme + theme(axis.title.x=element_text(size=16),
                          axis.text.x=element_text(size=16, angle=270),
                          strip.text.y=element_text(size=20, angle=270),
                          legend.position="top")
p

```

#### Total accesses per user
<<<<<<< HEAD
```{r fig.width=20, fig.height=6, include=TRUE, eval=TRUE}
plotdata <- data.browse %>%
  count(userName) %>%
  filter(n > 10) %>% 
  ungroup() %>% 
  left_join(data.browse[, c("userName", "teamName")]) %>% 
  mutate(userName=reorder(userName, n, ordered=TRUE))

pUser <- ggplot(plotdata, aes(x=userName, y=n)) 
pUser <- pUser + geom_point(aes(color=teamName), size=3)
pUser <- pUser + scale_y_log10()
pUser <- pUser + scale_color_brewer(palette = "Set1")

pUser <- pUser + mytheme + theme(axis.text.x=element_blank())
# pUser <- pUser + mytheme + theme(axis.text.x=element_text(angle=270, hjust=0.5))
pUser <- pUser + labs(x="User")
pUser
```

#### Entity Usage (more than 5 accesses)
```{r include=TRUE, eval=TRUE}
### Data
dataaccessCount <- data.browse %>%
  count(id, NAME, NODE_TYPE) %>% 
  filter(n > 5, !str_detect(id, "acl")) %>%
  ungroup() %>% 
  arrange(desc(n))
dataaccessCount %>% select(id, NAME, NODE_TYPE, n) %>% kable
=======

```{r fig.width=20, fig.height=6, include=TRUE, eval=TRUE}
plotdata <- data.browse %>%
  count(username) %>%
  filter(n > 10) %>% 
  ungroup() %>% 
  left_join(data.browse[, c("username", "group")]) %>% 
  mutate(username=reorder(username, n, ordered=TRUE))

pUser <- ggplot(plotdata, aes(x=username, y=n)) 
pUser <- pUser + geom_point(aes(color=group), size=3)
pUser <- pUser + scale_y_log10()
pUser <- pUser + mytheme + theme(axis.text.x=element_blank())
pUser <- pUser + labs(x="User")
pUser
```
```{r loadtop100, include=TRUE, eval=TRUE}
### Data
dataaccessCount <- data.browse %>%
  filter(!(NODE_TYPE == "project")) %>% 
  count(id, NAME, NODE_TYPE) %>% 
  filter(n > 1, !str_detect(id, "acl")) %>%
  ungroup() %>%
  mutate(id=reorder(id, desc(n), ordered=TRUE)) %>% 
  arrange(desc(n))
```

#### Popular entities

```{r plot100files, fig.width=20, fig.height=6, include=TRUE, eval=TRUE}
plotdata <- dataaccessCount %>% 
  filter(n > 5)

p <- ggplot(plotdata, aes(x=id, y=n))
p <- p + geom_bar(stat="identity", aes(fill=NODE_TYPE))
p <- p + facet_wrap(~ NODE_TYPE, scales="free", nrow = 3)
p <- p + mytheme
p <- p + theme(axis.text.x=element_text(size=10, angle=270, 
                                        vjust=0.5),
               axis.title.x=element_blank())
p
```
```{r include=TRUE, eval=TRUE}
plotdata %>% select(id, NAME, NODE_TYPE, n) %>% kable
>>>>>>> c68ab9da55b2d6b7b530442f7e96d14e671dfc3c
```