---
output: 
  html_document: 
    keep_md: yes
params:
  projectId: !r 'syn2775243'
  nMonths: !r NA
  useTeamGrouping: !r TRUE
  aclTeamOrder: !r c('syn2775243')
  queryDataFile: !r NA
  dataOutput: !r NA
  configFile: "~/datawarehouse_config.yml"
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(synapseClient)
library(RMySQL)
library(yaml)
source("lib.R")

synapseLogin()

options(xtable.type="html")

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  fig.width=20)

```

```{r config}
config <- yaml.load_file(params$configFile)

projectId <- gsub("syn", "", params$projectId)
proj <- synGet(params$projectId)


if (is.na(params$nMonths)) {
  startDate <- lubridate::as_date(proj@properties$createdOn)
  thisDate <- lubridate::floor_date(lubridate::today(), "month")
  thisDate <- thisDate - lubridate::period(1, "months")
  nMonths <- lubridate::interval(startDate, thisDate) %/% months(1)
} else {
  nMonths <- params$nMonths
}

useTeamGrouping <- params$useTeamGrouping
aclTeamOrder <- params$aclTeamOrder

if (useTeamGrouping) {
  aclUserList <- processAclUserList(projectId, aclTeamOrder)
} else {
  aclUserList <- NULL
}

con <- dbConnect(MySQL(),
                 user = config$username,
                 password = config$password,
                 host = config$host,
                 dbname='warehouse')

timestampBreaksDf <- makeDateBreaks(nMonths) %>% dplyr::arrange(date)


```

```{r domysqlquery}
queryDataPageviews <- getData(conn=con, templateName="pageViewTemplate", 
                              projectId=projectId,
                              timestampBreaksDf=timestampBreaksDf,
                              tempTableName="PROJECT_STATS")

queryDataPageviewsProcessed <- queryDataPageviews %>% 
  dplyr::mutate(recordType='pageview') %>% 
  processUsageStatsQueryData() %>%
  addUsers(., useTeamGrouping, aclUserList)

queryDataDownloads <- getData(conn=con, templateName='downloadTemplate', 
                              projectId=projectId,
                              timestampBreaksDf=timestampBreaksDf,
                              tempTableName="PROJECT_STATS")

queryDataDownloadsProcessed <- queryDataDownloads %>% 
  dplyr::mutate(recordType='download') %>% 
  processUsageStatsQueryData() %>%
  addUsers(., useTeamGrouping, aclUserList)


queryDataFDR <- getData(conn=con, templateName='FDRTemplate', 
                        projectId=projectId,
                        timestampBreaksDf=timestampBreaksDf,
                        tempTableName="PROJECT_STATS")

queryDataFDRProcessed <- queryDataFDR %>% 
  dplyr::mutate(recordType='download') %>% 
  processUsageStatsQueryData() %>%
  addUsers(., useTeamGrouping, aclUserList)


queryData <- rbind(queryDataPageviewsProcessed, 
                   queryDataDownloadsProcessed,
                   queryDataFDRProcessed)

if (!is.na(params$dataOutput)) {
  write.csv(queryData, file=params$dataOutput, row.names = FALSE)
}
```
### Activity on Synapse project `r proj@properties$name` (`r params$projectId`) from `r min(timestampBreaksDf$date)` to `r max(timestampBreaksDf$date)`.

#### Active new and unique registered Synapse users per month, starting from first month in the range:
```{r}
newUsers <- firstMonthToVisit(queryData) %>% mutate(source='New')
uniqueUsers <- uniqueUsersPerMonth(queryData) %>% mutate(source='Unique')

rbind(newUsers, uniqueUsers) %>% 
  reshape2::dcast(source ~ Date, value.var='Users') %>%
  knitr::kable()

```

#### Active registered Synapse users per team (per month):
```{r}
queryData %>% 
  select(dateGrouping, teamName, userName) %>% 
  filter(teamName != "Anonymous") %>%
  distinct() %>% 
  count(dateGrouping, teamName) %>% 
  reshape2::dcast(teamName ~ dateGrouping, value.var='n') %>% 
  knitr::kable()
```

There are `r length(setdiff(unique(queryData$userName), c("anonymous")))` active registered Synapse users in this time period. Of these, `r multiMonthVisits(queryData) %>% nrow` users were active in the project in at least two different months.

## Project page views

Count of the number of page views of the main project Wiki (`r params$projectId`) per month.

```{r}
projectPageViews <- queryData %>% filter(recordType=='pageview', NODE_TYPE=='project', id==projectId)

if (nrow(projectPageViews) > 0) {
  if (useTeamGrouping) {
    projectPageViewsCount <- projectPageViews %>%
      dplyr::filter(recordType == 'pageview') %>% 
      dplyr::count(teamName, dateGrouping) %>% 
      reshape2::dcast(teamName ~ dateGrouping, fun.aggregate = sum)
  } else {
    projectPageViewsCount <- projectPageViews %>%
      dplyr::filter(recordType == 'pageview') %>% 
      dplyr::mutate(teamName='All') %>% 
      dplyr::count(teamName, dateGrouping) %>% 
      reshape2::dcast(teamName ~ dateGrouping)
  }
  
  projectPageViewsCount %>% knitr::kable()
}

```

#### Page views per month

Count of the page views of any page (Wiki or entity) in the entire project per month.

```{r loadpermonth, include=TRUE, eval=TRUE}
if (useTeamGrouping) {
  dateGroupingCount <- queryData %>%
    dplyr::filter(recordType == 'pageview') %>% 
    dplyr::count(teamName, dateGrouping) %>% 
    reshape2::dcast(teamName ~ dateGrouping, fun.aggregate = sum)
} else {
  dateGroupingCount <- queryData %>%
    dplyr::filter(recordType == 'pageview') %>% 
    dplyr::mutate(teamName='All') %>% 
    dplyr::count(teamName, dateGrouping) %>% 
    reshape2::dcast(teamName ~ dateGrouping)
}

dateGroupingCount %>% knitr::kable()
```

#### Entity page views

The top 50 Files or Folders with at least 5 views.

```{r include=TRUE, eval=TRUE}
### Data
tmp <- queryData %>%
  dplyr::filter(recordType == 'pageview') %>% 
  dplyr::count(id, NAME, NODE_TYPE) %>% 
  dplyr::filter(n >= 5, !stringr::str_detect(id, "acl"))

if (nrow(tmp) > 0) {
  dataaccessCount1 <- queryData %>% 
    dplyr::filter(recordType == 'pageview') %>% 
    dplyr::filter(id %in% tmp$id) %>% 
    dplyr::count(id, NAME, NODE_TYPE, dateGrouping) %>% 
    dplyr::ungroup() %>%
    reshape2::dcast(id + NAME + NODE_TYPE ~ dateGrouping, value.var='n') %>% 
    dplyr::mutate(name=sprintf("<a href='https://www.synapse.org/#!Synapse:syn%s' target='_blank'>%s</a>", id, NAME))
  # dplyr::mutate(name=sprintf("[%s](https://www.synapse.org/#!Synapse:syn%s)", NAME, id))
  
  
  dataaccessCount2 <- queryData %>% 
    dplyr::filter(recordType == 'pageview') %>% 
    dplyr::filter(id %in% tmp$id) %>% 
    dplyr::count(id, NAME, NODE_TYPE) %>% 
    dplyr::ungroup() %>%
    dplyr::arrange(dplyr::desc(n))
  
  dataaccessCount <- dataaccessCount1 %>% 
    left_join(dataaccessCount2, by=c("id", "NAME", "NODE_TYPE")) %>% 
    dplyr::arrange(dplyr::desc(n)) %>%
    head(50) %>% 
    dplyr::rename(total=n) %>% 
    dplyr::select(name, everything(), total, -id, -NAME)
  
  dataaccessCount %>% DT::datatable(options=list(pageLength=20), escape=1)
}
```

#### Entity downloads (top 100 with more than 5 views)

The top 50 Files or Folders with at least 5 views.

```{r include=TRUE, eval=TRUE}
### Data
tmp <- queryData %>%
  dplyr::filter(recordType == 'download') %>% 
  dplyr::count(id, NAME, NODE_TYPE) %>% 
  dplyr::filter(n >= 5, !stringr::str_detect(id, "acl"))

if (nrow(tmp) > 0) {
  dataaccessCount1 <- queryData %>% 
    dplyr::filter(recordType == 'download') %>% 
    dplyr::filter(id %in% tmp$id) %>% 
    dplyr::count(id, NAME, NODE_TYPE, dateGrouping) %>% 
    dplyr::ungroup() %>%
    reshape2::dcast(id + NAME + NODE_TYPE ~ dateGrouping, value.var='n') %>% 
    dplyr::mutate(name=sprintf("<a href='https://www.synapse.org/#!Synapse:syn%s' target='_blank'>%s</a>", id, NAME))
  # dplyr::mutate(name=sprintf("[%s](https://www.synapse.org/#!Synapse:syn%s)", NAME, id))
  
  
  dataaccessCount2 <- queryData %>% 
    dplyr::filter(recordType == 'download') %>% 
    dplyr::filter(id %in% tmp$id) %>% 
    dplyr::count(id, NAME, NODE_TYPE) %>% 
    dplyr::ungroup() %>%
    dplyr::arrange(dplyr::desc(n))
  
  dataaccessCount <- dataaccessCount1 %>% 
    left_join(dataaccessCount2, by=c("id", "NAME", "NODE_TYPE")) %>% 
    dplyr::arrange(dplyr::desc(n)) %>%
    head(50) %>% 
    dplyr::rename(total=n) %>% 
    dplyr::select(name, everything(), total, -id, -NAME)
  
  dataaccessCount %>% DT::datatable(options=list(pageLength=20), escape=1)
}
```
