---
output: 
  html_document: 
    keep_md: yes
params:
  projectId: !r 'syn2580853'
  nMonths: 6
  useTeamGrouping: FALSE
  aclTeamOrder: !r c('syn2580853')
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(synapseClient)
library(RMySQL)
library(yaml)

source("lib.R")

synapseLogin()

options(xtable.type="html")

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  fig.width=20)

qTemplate <- 'select NORMALIZED_METHOD_SIGNATURE,PROJECT_ID,BENEFACTOR_ID,PARENT_ID,ENTITY_ID,CONVERT(AR.TIMESTAMP, CHAR) AS TIMESTAMP,RESPONSE_STATUS,DATE,USER_ID,NODE_TYPE,N.NAME from ACCESS_RECORD AR, PROCESSED_ACCESS_RECORD PAR, NODE_SNAPSHOT N, (select distinct ID from NODE_SNAPSHOT where PROJECT_ID = "%s") NODE where AR.TIMESTAMP Between %s AND %s and AR.SESSION_ID = PAR.SESSION_ID and AR.TIMESTAMP = PAR.TIMESTAMP and PAR.ENTITY_ID = NODE.ID and N.ID = NODE.ID and CLIENT = "WEB" AND (PAR.NORMALIZED_METHOD_SIGNATURE = "GET /entity/#/bundle" OR PAR.NORMALIZED_METHOD_SIGNATURE = "GET /entity/#/version/#/bundle" OR PAR.NORMALIZED_METHOD_SIGNATURE = "GET /entity/#/wiki2" OR PAR.NORMALIZED_METHOD_SIGNATURE = "GET /entity/#/wiki2/#");'

```

```{r config}
config <- yaml.load_file("mysql_config.yml")

projectId <- gsub("syn", "", params$projectId)
nMonths <- params$nMonths
useTeamGrouping <- params$useTeamGrouping
aclTeamOrder <- params$aclTeamOrder

con <- dbConnect(MySQL(),
                 user = config$username,
                 password = config$password,
                 host = config$host,
                 dbname='warehouse')

timestampBreaksDf <- makeDateBreaks(nMonths)

```

```{r domysqlquery}
queryData <- getData(con=con, qTemplate=qTemplate, projectId=projectId,
                     timestampBreaksDf=timestampBreaksDf)

```
### Usage from `r min(timestampBreaksDf$beginTime)` to `r max(timestampBreaksDf$endTime)`.

```{r users}
if (useTeamGrouping) {
  aclUserList <- processAclUserList(projectId, aclTeamOrder)
} else {
  aclUserList <- NULL
}
```

```{r summaryuseraccess}
# Get user profile info for users in data download records

allUsers <- getQueryUserProfiles(queryData, useTeamGrouping, aclUserList)

```

```{r userJoin}
queryData <- queryData %>%
  left_join(., allUsers)
```

#### Total Users
There are `r length(setdiff(unique(queryData$userName), c("anonymous")))` active users in this time period. 

#### Returning users
`r multiMonthVisits(queryData) %>% nrow` users have viewed a page in at least two different months.

#### New users (per month, starting from first month in the range):
```{r}
firstMonthToVisit(queryData) %>% kable
```

#### Unique users (per month, starting from first month in the range):
```{r}
uniqueUsersPerMonth(queryData) %>% 
  #mutate(Date=paste(month(Date, label=TRUE), year(Date))) %>%
  kable
```

#### Website access per month
```{r loadpermonth, include=TRUE, eval=TRUE}
if (useTeamGrouping) {
  dateGroupingCount <- queryData %>%
    dplyr::count(teamName, dateGrouping) %>% 
    reshape2::dcast(teamName ~ dateGrouping, fun.aggregate = sum)
} else {
  dateGroupingCount <- queryData %>%
    dplyr::mutate(teamName='All') %>% 
    dplyr::count(teamName, dateGrouping) %>% 
    reshape2::dcast(teamName ~ dateGrouping)
}

dateGroupingCount %>% kable
```

#### Website access per day
```{r loadperday, include=TRUE, eval=TRUE}
### Daily usage
# queryData <- queryData %>%
#   mutate(date=as.Date(as.character(DATE)),
#          userId=as.character(userid)) %>% 
#   left_join(., allUsers)

perdayCount <- countByDay(queryData, useTeamGrouping)
```

```{r plotperday, fig.width=20, fig.height=6, include=TRUE, eval=TRUE}
### Per day usage, total

plotByDay(perdayCount, useTeamGrouping)
```

#### Views per user (top 20 users)
```{r peruser}
plotdata <- queryData %>%
  dplyr::count(userName) %>%
  # filter(n > 1) %>% 
  dplyr::ungroup() %>% 
  dplyr::left_join(allUsers) %>% 
  dplyr::mutate(userName=reorder(userName, n, ordered=TRUE))

plotdata %>% 
  dplyr::top_n(20, n) %>% 
  dplyr::arrange(-n) %>% 
  dplyr::select(n) %>% 
  kable(row.names=TRUE)
```

#### Entity Usage (more than 5 accesses)
```{r include=TRUE, eval=TRUE}
### Data
dataaccessCount <- queryData %>%
  dplyr::count(id, NAME, NODE_TYPE) %>% 
  dplyr::filter(n > 5, !str_detect(id, "acl")) %>%
  dplyr::ungroup() %>% 
  dplyr::arrange(desc(n))

dataaccessCount %>% 
  dplyr::select(id, NAME, NODE_TYPE, n) %>% 
  head(50) %>% 
  kable
```